Correlation analysis to inferred infection rates (deconvolved case rates)

### 2021-06-05 survey/code/deconv_corr.Rmd
Updated deconv experiments

cases <- covidcast_signal(data_source = "usa-facts",
                           signal = "confirmed_7dav_incidence_prop",
                           start_day = "2020-04-15",
                           end_day = "2021-04-15", 
                           geo_type = "state")
survey <- covidcast_signal(data_source = "fb-survey",
                           signal = "smoothed_whh_cmnty_cli",
                           start_day = "2020-04-15",
                           end_day = "2021-04-15", 
                           geo_type = "state")

@@

```{r}
# Compute correlation per time, over all counties
cor_geowise1 <- covidcast_cor(deconv, survey, by = "time_value")
cor_geowise2 <- covidcast_cor(cases, survey, by = "time_value")
cor_geowise <- rbind(cor_geowise1, cor_geowise2)
cor_geowise$signal = as.factor(
  c(rep("deconv-survey", nrow(cor_geowise1)),
    rep("cases-survey", nrow(cor_geowise2))))

@@

```{r}
# Compute correlation per location, over all time
cor_timewise1 <- covidcast_cor(deconv, survey, by = "geo_value")
cor_timewise2 <- covidcast_cor(cases, survey, by = "geo_value")
cor_timewise <- rbind(cor_timewise1, cor_timewise2)
cor_timewise$signal = as.factor(
  c(rep("deconv-survey", nrow(cor_timewise1)),
    rep("cases-survey", nrow(cor_timewise2))))

@@

```{r}
# Loop over values for dt, and compute correlations per state
dt_vec <- (-20):10
cor_timewise_list1 <- vector("list", length(dt_vec))
for (i in 1:length(dt_vec)) {
  cor_timewise_list1[[i]] <- covidcast_cor(deconv, survey, dt_x = dt_vec[i],
                               by = "geo_value")
  cor_timewise_list1[[i]]$dt <- dt_vec[i]
}

# Stack into one big data frame, and then plot the median correlation by dt
cor_timewise_dt1 <- do.call(rbind, cor_timewise_list1)
cor_timewise_dt1 %>%
  group_by(dt) %>%
  summarize(value = mean(value, na.rm = TRUE), .groups = "drop_last") %>%
  ggplot(aes(x = dt, y = value)) + geom_line() + geom_point() +
  labs(x = "dt", y = "Correlation") + theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank())
```

```{r}
# Loop over values for dt, and compute correlations per state
cor_timewise_list2 <- vector("list", length(dt_vec))
for (i in 1:length(dt_vec)) {
  cor_timewise_list2[[i]] <- covidcast_cor(cases, survey, dt_x = dt_vec[i],
                               by = "geo_value")
  cor_timewise_list2[[i]]$dt <- dt_vec[i]
}

# Stack into one big data frame, and then plot the median correlation by dt
cor_timewise_dt2 <- do.call(rbind, cor_timewise_list2)
cor_timewise_dt2 %>%
  group_by(dt) %>%
  summarize(value = mean(value, na.rm = TRUE), .groups = "drop_last") %>%
  ggplot(aes(x = dt, y = value)) + geom_line() + geom_point() +
  labs(x = "dt", y = "Correlation") + theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank())
```

>>>>

start_day <- "2020-04-15"
end_day <- "2021-04-15"
geo_type <- "state"
cli <- covidcast_signal(data_source = "fb-survey",
                        signal = "smoothed_wcli",
                        start_day, end_day, geo_type)
cmt <- covidcast_signal(data_source = "fb-survey",
                        signal = "smoothed_whh_cmnty_cli",
                        start_day, end_day, geo_type)
cases <- covidcast_signal(data_source = "usa-facts",
                          signal = "confirmed_7dav_incidence_prop",
                        start_day, end_day, geo_type)

@@

```{r}
# Compute correlation per time, over all counties
by = "time_value"
cor_geowise <- rbind(
  data.frame(covidcast_cor(cli, deconv, by = by), signal = "cli-deconv"),
  data.frame(covidcast_cor(cmt, deconv, by = by), signal = "cmt-deconv"),
  data.frame(covidcast_cor(cli, cases, by = by), signal = "cli-cases"),
  data.frame(covidcast_cor(cmt, cases, by = by), signal = "cmt-cases"))

@@

```{r}
# Compute correlation per location, over all time
by <- "geo_value"
cor_timewise <- rbind(
  data.frame(covidcast_cor(cli, deconv, by = by), signal = "cli-deconv"),
  data.frame(covidcast_cor(cmt, deconv, by = by), signal = "cmt-deconv"),
  data.frame(covidcast_cor(cli, cases, by = by), signal = "cli-cases"),
  data.frame(covidcast_cor(cmt, cases, by = by), signal = "cmt-cases"))

@@

```{r}
# Loop over values for dt, and compute correlations per state
dt_vec <- (-20):20
by <- "geo_value"
cor_timewise_list <- vector("list", length(dt_vec))
for (i in 1:length(dt_vec)) {
  cor_timewise_list[[i]] <- rbind(
    data.frame(covidcast_cor(cli, deconv, dt_x = dt_vec[i], by = by), 
               dt = dt_vec[i], signal = "cli-deconv"),
    data.frame(covidcast_cor(cmt, deconv, dt_x = dt_vec[i], by = by), 
               dt = dt_vec[i], signal = "cmt-deconv"),
    data.frame(covidcast_cor(cli, cases, dt_x = dt_vec[i], by = by), 
               dt = dt_vec[i], signal = "cli-cases"),
    data.frame(covidcast_cor(cmt, cases, dt_x = dt_vec[i], by = by), 
               dt = dt_vec[i], signal = "cmt-cases"),
    data.frame(covidcast_cor(cli, cmt, dt_x = dt_vec[i], by = by), 
               dt = dt_vec[i], signal = "cli-cmt"))
}

# Stack into one big data frame, and then plot the mean correlation by dt
cor_timewise_dt <- do.call(rbind, cor_timewise_list)
cor_timewise_dt %>%
  group_by(dt, signal) %>%
  summarize(value = mean(value, na.rm = TRUE), .groups = "drop_last") %>%
  ggplot(aes(x = dt, y = value)) + 
  geom_line(aes(color = signal)) + geom_point(aes(color = signal)) +
  labs(x = "dt", y = "Correlation") + theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank())

cor_timewise_dt %>%
  group_by(dt, signal) %>%
  summarize(value = median(value, na.rm = TRUE), .groups = "drop_last") %>%
  ggplot(aes(x = dt, y = value)) + 
  geom_line(aes(color = signal)) + geom_point(aes(color = signal)) +
  labs(x = "dt", y = "Correlation") + theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank())
```
